Run Life expectancy and decomposition calculations

### 2017-01-20 Code/2_Run_LE_and_Decomp_Calcs.Rmd

```{r load_data}
dat.aggregated <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", header = T)
dat.clean<- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", header = T)
```

@@

#stopped here!

@@

@@

      if(any(is.na(ct.both$prop.black1)) == F & any(is.na(ct.both$prop.white1)) == F) { #ensures that there are no ages with 0 deaths - for these COD prop == 0 and can't compute

        list.cod.decomp.tables1[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables1[[black.index]]),
                                                              life.table2 = as.data.frame(list.life.tables1[[white.index]]), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables1[[i]]),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white1, prop.black1), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black1", 
                                                              prop2.colname.cod.table = "prop.white1")

        list.cod.decomp.tables5[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white5, prop.black5), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black5", 
                                                              prop2.colname.cod.table = "prop.white5")

        list.cod.decomp.tables9[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white9, prop.black9), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black9", 
                                                              prop2.colname.cod.table = "prop.white9")

      } else { list.cod.decomp.tables[[i]] <- list.cod.decomp.tables5[[i]] <- list.cod.decomp.tables9[[i]] <- "Encountered age group with no deaths"

@@

      list.cod.decomp.tables[[i]] <- list.cod.decomp.tables5[[i]] <- list.cod.decomp.tables9[[i]] <- "Couldn't compare life tables"
    }

>>>>

```{r load_data}
dat.aggregated <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.Rdata", header = T)
dat.clean<- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.Rdata", header = T)
```

@@

@@

    list.cod.decomp.tables1[[i]]$StateYearSex <- paired.ids[i, "StateYearSex"]
    list.cod.decomp.tables5[[i]]$StateYearSex <- paired.ids[i, "StateYearSex"]
    list.cod.decomp.tables9[[i]]$StateYearSex <- paired.ids[i, "StateYearSex"]

@@

      if(!any(is.na(ct.both$prop.black1)) & !any(is.na(ct.both$prop.white1))) { #ensures that there are no ages with 0 deaths - for these COD prop == 0 and can't compute

        list.cod.decomp.tables1[[i]]$decomp.table <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables1[[black.index]]$life.table),
                                                              life.table2 = as.data.frame(list.life.tables1[[white.index]]$life.table), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables1[[i]]$decomp.table),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white1, prop.black1), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black1", 
                                                              prop2.colname.cod.table = "prop.white1")

        list.cod.decomp.tables5[[i]]$decomp.table <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]$life.table),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]$life.table), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]$decomp.table),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white5, prop.black5), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black5", 
                                                              prop2.colname.cod.table = "prop.white5")

        list.cod.decomp.tables9[[i]]$decomp.table <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]$life.table),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]$life.table), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]$decomp.table),
                                                              cod.table = ct.both %>% select(Age_factor, COD_factor, prop.white9, prop.black9), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black9", 
                                                              prop2.colname.cod.table = "prop.white9")

      } else { list.cod.decomp.tables1[[i]]$decomp.table <- list.cod.decomp.tables5[[i]]$decomp.table <- list.cod.decomp.tables9[[i]]$decomp.table <- "Encountered age group with no deaths"

@@

      list.cod.decomp.tables1[[i]]$decomp.table <- list.cod.decomp.tables5[[i]]$decomp.table <- list.cod.decomp.tables9[[i]]$decomp.table <- "Couldn't compare life tables"
    }
